Compositional Certified Resource Bounds\ifshort{\vspace{-.15cm}}{}

### 2014-09-09 paper/main.tex

\sectskip
\section{Conclusion}
\label{sec:concl}
\aftersectskip

@@

@@

\begin{figure*}[t]
  \centering
  \footnotesize
  \begin{mathpar}
  \inferrule*[right={\scriptsize (Q:Loop)},leftskip=0cm,rightskip=0cm,width=20cm]
  { \inferrule*[right={\scriptsize (Q:If)},leftskip=0cm,rightskip=0cm,width=20cm]
    { 
      \inferrule*[right={\scriptsize (Q:Weak)},leftskip=2cm,rightskip=4cm, vdots=1.5cm]
      { 
        \inferrule*[right={\scriptsize (Q:Seq)},leftskip=0cm,rightskip=0cm]
        {
\inferrule*[right={\scriptsize (Q:Weak)},leftskip=0cm,rightskip=0cm]
{
  \inferrule*[right={\scriptsize (Q:DecP)},leftskip=0cm,rightskip=0cm]
  { }
  {(x {<} 10, B^\text{de}); ((x {\geq} 10,Q^\text{de})  \vdash \code{x = x - 10}
   \dashv (\cdot, P^\text{de})
  }
}
{(x {<} 10, B^\text{we}); ((x {\geq} 10,Q^\text{we})  \vdash \code{x = x - 10}
\dashv (\cdot, P^\text{we})
}
\and
\inferrule*[right={\scriptsize (Q:Tick)},leftskip=0cm,rightskip=0cm]
{ }
{(x {<} 10, B^\text{ti}); (\cdot,Q^\text{ti})  \vdash \code{tick(5)}
 \dashv (\cdot, P^\text{ti})
}
} {
          (x {<} 10, B^\text{sq}); ((x {\geq} 10,Q^\text{sq}) \vdash \code{x=x{-}10; tick(5);} \dashv (\cdot,P^\text{sq}) 
        }
      }
      { (x {<} 10, B^\text{if}); ((x {\geq} 10,Q^\text{if}) \vdash \code{x=x{-}10; tick(5);} \dashv (\cdot,P^\text{if}) }
      \and
      \inferrule*[right={\scriptsize (Q:Weak)},leftskip=4.5cm,rightskip=4cm]
      { \inferrule*[right={\scriptsize (Q:Break)},leftskip=0cm,rightskip=0cm]
        { }
        {(x {<} 10, B^\text{br}); (x {<} 10,Q^\text{br}) \vdash \code{break} \dashv (\bot,P^\text{br})}
      }
      {
        (x {<} 10, B^\text{el}); (x {<} 10,Q^\text{el}) \vdash \code{break} \dashv (\cdot,P^\text{el})
      }
    }
    { \hspace{3cm} (x {<} 10, B^\text{lo}); (\cdot,Q^\text{lo}) \vdash \loopbody \dashv (\cdot,P^\text{lo}) \hspace{3cm} 
    }
  }
  {
   (\cdot, B); (\cdot, Q) \vdash \code{loop}~{\loopbody} \dashv (x {<} 10, P) 
  }
\end{mathpar}
\flushleft Constraints:
$$
\begin{array}{llll}
P = B^\text{lo} & Q  = Q^\text{lo} & Q^\text{lo} = P^\text{lo} \\
B^\text{el} = B^\text{if} = B^\text{lo} & Q^\text{el} = Q^\text{if} = Q^\text{lo} & P^\text{el} = P^\text{if} = P^\text{lo} \\
B^\text{el} = B^\text{br}  & Q^\text{el} \succeq_{(x{<}10)} Q^\text{br}  & P^\text{br} \succeq_{(\cdot)} P^\text{el} \\
B^\text{br} = Q^\text{br}\\
B^\text{if} = B^\text{sq}  & Q^\text{if} \succeq_{(x{<}10)} Q^\text{sq}  & P^\text{sq} \succeq_{(\cdot)} P^\text{if} \\
B^\text{sq} = B^\text{we} = B^\text{ti} & Q^\text{sq} = Q^\text{we} & P^\text{we} = Q^\text{ti} & P^\text{ti} = P^\text{sq} \\
Q^\text{ti} = P^\text{ti} + 5 \\
B^\text{we} = B^\text{de}  & Q^\text{we} \succeq_{(x{<}10)} Q^\text{de}  & P^\text{de} \succeq_{(\cdot)} P^\text{we} \\
p^\text{de}_{0,10} = q^\text{de}_{0,10} + q^\text{de}_{0,x}  & p^\text{de}_{0} = q^\text{de}_{0}
& \forall (\alpha, \beta) \neq (0,10)  . \, p^\text{de}_{\alpha,\beta} = q^\text{de}_{\alpha,\beta}
\end{array}
$$
\flushleft Linear Objective Function:
$$
q_{x,0} + 10000{\cdot}q_{0,x} + 10{\cdot}q_{x,10} + 9990q_{10,x}
$$
\flushleft Constant Objective Function:
$$
q_0 + 11{\cdot}q_{0,10}  
$$
\caption{An example derivation as produced by the automatic tool.}
\label{fig:derivation}
\end{figure*}

@@

The LP solver now returns a solution of the constraint set and an
objective value, that is, a mapping from variables to floating-point
numbers and the value of the objective function with this
instantiation.  The solver also memorizes the optimization path that
lead to the optimal solution.  In this case, the objective value would
be
$$
5000
$$
since the LP solver assigns $q_{0,x} = 0.5$ and $q_{*} = 0$ otherwise.
We now add the constraint
$$
q_{x,0} + 10000{\cdot}q_{0,x} + 10{\cdot}q_{x,10} + 9990q_{10,x} = 5000
$$
to our constraint set and ask the solver to optimize the objective
function
$$
q_0 + 11{\cdot}q_{0,10} \; .
$$
This happens in almost no time in practice.

>>>>

\begin{figure*}[t]
  \centering
  \footnotesize
  \begin{mathpar}
  \inferrule*[right={\scriptsize (Q:Loop)},leftskip=0cm,rightskip=0cm,width=20cm]
  { \inferrule*[right={\scriptsize (Q:If)},leftskip=0cm,rightskip=0cm,width=20cm]
    { 
      \inferrule*[right={\scriptsize (Q:Weak)},leftskip=2cm,rightskip=4cm, vdots=1.5cm]
      { 
        \inferrule*[right={\scriptsize (Q:Seq)},leftskip=0cm,rightskip=0cm]
        {
\inferrule*[right={\scriptsize (Q:Weak)},leftskip=0cm,rightskip=0cm]
{
  \inferrule*[right={\scriptsize (Q:DecP)},leftskip=0cm,rightskip=0cm]
  { }
  {(x {<} 10, B^\text{de}); ((x {\geq} 10,Q^\text{de})  \vdash \code{x = x - 10}
   \dashv (\cdot, P^\text{de})
  }
}
{(x {<} 10, B^\text{we}); ((x {\geq} 10,Q^\text{we})  \vdash \code{x = x - 10}
\dashv (\cdot, P^\text{we})
}
\and
\inferrule*[right={\scriptsize (Q:Tick)},leftskip=0cm,rightskip=0cm]
{ }
{(x {<} 10, B^\text{ti}); (\cdot,Q^\text{ti})  \vdash \code{tick(5)}
 \dashv (\cdot, P^\text{ti})
}
} {
          (x {<} 10, B^\text{sq}); ((x {\geq} 10,Q^\text{sq}) \vdash \code{x=x{-}10; tick(5);} \dashv (\cdot,P^\text{sq}) 
        }
      }
      { (x {<} 10, B^\text{if}); ((x {\geq} 10,Q^\text{if}) \vdash \code{x=x{-}10; tick(5);} \dashv (\cdot,P^\text{if}) }
      \and
      \inferrule*[right={\scriptsize (Q:Weak)},leftskip=4.5cm,rightskip=4cm]
      { \inferrule*[right={\scriptsize (Q:Break)},leftskip=0cm,rightskip=0cm]
        { }
        {(x {<} 10, B^\text{br}); (x {<} 10,Q^\text{br}) \vdash \code{break} \dashv (\bot,P^\text{br})}
      }
      {
        (x {<} 10, B^\text{el}); (x {<} 10,Q^\text{el}) \vdash \code{break} \dashv (\cdot,P^\text{el})
      }
    }
    { \hspace{3cm} (x {<} 10, B^\text{lo}); (\cdot,Q^\text{lo}) \vdash \loopbody \dashv (\cdot,P^\text{lo}) \hspace{3cm} 
    }
  }
  {
   (\cdot, B); (\cdot, Q) \vdash \code{loop}~{\loopbody} \dashv (x {<} 10, P) 
  }
\end{mathpar}
\flushleft Constraints:
$$
\begin{array}{llll}
P = B^\text{lo} & Q  = Q^\text{lo} & Q^\text{lo} = P^\text{lo} \\
B^\text{el} = B^\text{if} = B^\text{lo} & Q^\text{el} = Q^\text{if} = Q^\text{lo} & P^\text{el} = P^\text{if} = P^\text{lo} \\
B^\text{el} = B^\text{br}  & Q^\text{el} \succeq_{(x{<}10)} Q^\text{br}  & P^\text{br} \succeq_{(\cdot)} P^\text{el} \\
B^\text{br} = Q^\text{br}\\
B^\text{if} = B^\text{sq}  & Q^\text{if} \succeq_{(x{<}10)} Q^\text{sq}  & P^\text{sq} \succeq_{(\cdot)} P^\text{if} \\
B^\text{sq} = B^\text{we} = B^\text{ti} & Q^\text{sq} = Q^\text{we} & P^\text{we} = Q^\text{ti} & P^\text{ti} = P^\text{sq} \\
Q^\text{ti} = P^\text{ti} + 5 \\
B^\text{we} = B^\text{de}  & Q^\text{we} \succeq_{(x{<}10)} Q^\text{de}  & P^\text{de} \succeq_{(\cdot)} P^\text{we} \\
p^\text{de}_{0,10} = q^\text{de}_{0,10} + q^\text{de}_{0,x}  & p^\text{de}_{0} = q^\text{de}_{0}
& \forall (\alpha, \beta) \neq (0,10)  . \, p^\text{de}_{\alpha,\beta} = q^\text{de}_{\alpha,\beta}
\end{array}
$$
\vspace{1.5ex}

\begin{tabular}{l@{\hspace{5em}}l}
 Linear Objective Function: &  Constant Objective Function: \\
\hspace{3em} $
q_{x,0} + 10000{\cdot}q_{0,x} + 10{\cdot}q_{x,10} + 9990q_{10,x}
$
&
\hspace{3em}
$
q_0 + 11{\cdot}q_{0,10}  
$
\end{tabular}

\caption{An example derivation as produced by the automatic tool.}
\label{fig:derivation}
\end{figure*}
\sectskip
\section{Conclusion}
\label{sec:concl}
\aftersectskip

@@

\newpage

@@

@@

The LP solver now returns a solution of the constraint set and an
objective value, that is, a mapping from variables to floating-point
numbers and the value of the objective function with this
instantiation.  The solver also memorizes the optimization path that
lead to the optimal solution.  In this case, the objective value would
be
$
5000
$
since the LP solver assigns $q_{0,x} = 0.5$ and $q_{*} = 0$ otherwise.
We now add the constraint
$$
q_{x,0} + 10000{\cdot}q_{0,x} + 10{\cdot}q_{x,10} + 9990q_{10,x} = 5000
$$
to our constraint set and ask the solver to optimize the objective
function
$$
q_0 + 11{\cdot}q_{0,10} \; .
$$
This happens in almost no time in practice.
